\textbf{Computational Fuzzy Extractors}

### 2013-05-09 trunk/CompFuzzExt.tex
Cleaning up references in introduction

\documentclass[11pt]{article}
\def\shownotes{1}

@@

Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.  
The minimal entropy loss is dictated by bounds on error-correcting codes.  Fuzzy extractors suffer from similar bounds imposed by coding theory.

@@

Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources.  (\bnote{Are these references for fuzzy extractors or secure sketches?} as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).  The setting 
%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).  The Generate ($\gen$) algorithm takes an input $w$ and produces a key $r$ and a public value $p$.  This information allows
the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close to $w$ (according to some predefined metric, such as Hamming distance). 
Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.  This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to reproduce the key $r$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.

@@

The main item I think needs to change is their Lemma 2.4
\begin{lemma}~\cite[Min-Entropy Version of Lemma 2.4]{micciancio2013hardness}
Let $\mathcal{L}$ be a family of functions on a common domain $X$ and let $Z$ be a distribution over $X$.  Then $(\mathcal{L}, Z)$ is $\epsilon$-uninvertible~(even statistically, with respect to computationally unbounded adversaries) for $\epsilon = \expe_{f\leftarrow \mathcal{L}} [|f(X)|]/ 2^{-H_\infty(Z)}$.
\end{lemma}
Fix a function $f$.  The best way to predict $Z$ given $f(Z)$ is the average predictability of $Z | f(Z)$.  This predictability is $2^{-\Hav(Z | f(Z))}$.  By Lemma 2.2 of Dodis et.al.~\cite{DBLP:journals/siamcomp/DodisORS08}, 
\tilde{H}_\infty(Z | f(Z))\geq H_\infty(Z) - \log |f(Z)| \geq \Hoo(Z) - \log |f(X)|.
  The statement of the lemma follows by converting to predictability.
%\section{Computational Fuzzy Extractors}
%In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.  We begin with a formal definition of a computational fuzzy extractor:
%\label{sec:comp fuzzy extractors}
%Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
%\begin{lemma}
%Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.  Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.  Let, $s' = s_{sec}-s_{ext}$, then 
%$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
%%  the same paradigm from 
%%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).  It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.  However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).  
%%\begin{definition}
%%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.  Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
%%\end{definition}
%%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
%%\label{lem:unp extraction} 
%%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
%%\end{lemma}
%We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
%\begin{lemma}
%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.  Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.  Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
%%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
%%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
%%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
%%\end{lemma}
%%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
%%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.

>>>>

\documentclass[11pt]{article}
\def\shownotes{0}

@@

Secure sketches necessarily reveal some information about the noisy secret.
% and thus the key derived by fuzzy extractors has lower entropy than the source.  
The minimal entropy loss is dictated by bounds on error-correcting codes.  
Fuzzy extractors constructed using secure sketches suffer a similar entropy loss.  This entropy loss decreases the length of the derived key.  
%suffer from similar bounds imposed by coding theory.

@@

Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources~(see \cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy} for applications of fuzzy extractors).  The setting 
%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).  The Generate ($\gen$) algorithm takes an input $w$ and produces a key $r$ and a public value $p$.  This information allows
the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close to $w$ (according to some predefined metric, such as Hamming distance). 
Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.  This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to reproduce the key $r$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.

@@

The main item I think needs to change is their Lemma 2.4
\begin{lemma}~\cite[Min-Entropy Version of Lemma 2.4]{micciancio2013hardness}
Let $\mathcal{L}$ be a family of functions on a common domain $X$ and let $Z$ be a distribution over $X$.  Then $(\mathcal{L}, Z)$ is $\epsilon$-uninvertible~(even statistically, with respect to computationally unbounded adversaries) for $\epsilon = \expe_{f\leftarrow \mathcal{L}} [|f(X)|]/ 2^{-H_\infty(Z)}$.
\end{lemma}
\begin{proof}
Fix a function $f$.  The best way to predict $Z$ given $f(Z)$ is the average predictability of $Z | f(Z)$.  This predictability is $2^{-\Hav(Z | f(Z))}$.  By Lemma 2.2 of Dodis et.al.~\cite{DBLP:journals/siamcomp/DodisORS08}, 
\[
\tilde{H}_\infty(Z | f(Z))\geq H_\infty(Z) - \log |f(Z)| \geq \Hoo(Z) - \log |f(X)|.
\]
  The statement of the lemma follows by converting to predictability.
\end{proof}

%\section{Computational Fuzzy Extractors}
%In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.  We begin with a formal definition of a computational fuzzy extractor:
%\label{sec:comp fuzzy extractors}
%
%
%Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
%\begin{lemma}
%Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.  Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.  Let, $s' = s_{sec}-s_{ext}$, then 
%$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
%\end{lemma}
%%  the same paradigm from 
%%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).  It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.  However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).  
%%\begin{definition}
%%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.  Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
%%\end{definition}
%%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
%%\label{lem:unp extraction} 
%%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
%%\end{lemma}
%We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
%\begin{lemma}
%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.  Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.  Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
%\end{lemma}
%%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
%%\begin{itemize}
%%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
%%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
%%\end{itemize}
%%\end{lemma}
%%\begin{proof}
%%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
%%\end{proof}
%%
%%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.
